\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      % \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Ray Tsai} \\ \vspace{15pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:18589050735}{+1 (858) 905-0735}
    $\cdot$
    \faAt \hspace{.5pt} \href{mailto:raytsai919@gmail.com}{raytsai919@gmail.com}
    $\cdot$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/himetsai}{LinkedIn}
    $\cdot$
    \faGithub \hspace{.5pt} \href{https://github.com/himetsai}{GitHub}
    $\cdot$
    \faGlobe \hspace{.5pt} \href{https://himetsai.com}{Website}
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{8pt}
  \resumeSubHeadingListStart
    \resumeEducationHeading
      {University of California San Diego
      }{La Jolla, CA}
      {B.Sc. in Mathematics-Computer Science (GPA: 3.9/4.0)}{Sep 2021 \textbf{--} Jun 2025}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant coursework:} Honors Abstract Algebra, Honors Graph Theory, Graduate Level Statistical Learning, Probability Theory, Linear Algebra, Calculus, Data Structure, Game Theory.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{8pt}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {Department of Mathematics, University of California San Diego}{La Jolla, CA}
      {Undergraduate Research Assistant}{Apr 2023 \textbf{--} Present}
        \resumeItemListStart
            \resumeItem{Engaging in a rigorous study on extremal graph theory mentored by \href{https://annatar0.wixsite.com/website-4}{Prof. Jacques Verstraete}.}
            \resumeItem{Investigating an open problem on long-directed paths in Eulerian-directed graphs.}
            \resumeItem{Secured the research position based on top performance and highest grade achieved in the Honors Graph Theory course.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd


%----------- WORK EXPERIENCE -----------

\section{Work Experience}
  \vspace{8pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Micro-star International}{Taipei, Taiwan}
      {Software Engineer}{Jul 2023 \textbf{--} Aug 2023, Full-time}
        \resumeItemListStart
            \resumeItem{Collaborated with a 5-member team to develop a Windows-based application for local AI image generation and model training.}
            \resumeItem{Pioneered a custom model using Stable Diffusion, effectively generating images of MSI laptops.}
            \resumeItem{Architected and implemented an installation process for multiple optimizers, boosting image generation speeds by 80\%.}
        \resumeItemListEnd

    \resumeSubheading
      {Kook}{San Diego, CA}
      {Co-founder, Lead Software Engineer}{Dec 2021 \textbf{--} Dec 2022}
        \resumeItemListStart
            \resumeItem{Led a 5-member team in the creation of an automated surfboard rental station, incubated by UCSD Basement Blackstone LaunchPad and ECE Makerspace.}
            \resumeItem{Operated as a full-stack engineer, independently learning app development to architect the company's application, facilitating access to the surfboard station, and documenting the rental history.}
            \resumeItem{Innovated the station's unlock system by leveraging NFC technology, significantly enhancing the user experience.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Additional Experience}
  \vspace{7pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{\href{https://himetsai.com}{Personal Website}}{ A blogging website I built to document my life and refresh my chinese writing skills. (Dec 2022)} \\ \vspace{5pt}
    }}
    \small{\item{
        \textbf{UCSD Theory Group}{ Part of the UCSD theory group and attend various seminars and weekly meetings on theoretical computer science. } \\ \vspace{5pt}
    }}
    \small{\item{
        \textbf{William Lowell Putnam Mathematical Competition}{ Got 3 out of 120 possible points on the most prestigious undergraduate level math competition.} \\ \vspace{5pt}
    }}
  \resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
  \resumeSubHeadingListStart
    \small{\item{
        LaTeX, JavaScript(React Native, Next.js), Python(Flask, Selenium), C/C++, Java, Git
    }}
  \resumeSubHeadingListEnd

% ----------- HOBBIES -----------

\section{Hobbies}
  \resumeSubHeadingListStart
    \small{\item{Swimming, Chess, Electric Guitar, Math, Blogging, \href{https://www.linkedin.com/in/audrey-liang-2022/}{Audrey Liang}, Mario Kart, Super Smash Bros Ultimate}}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}