\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-2pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeEducationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-2pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge Ray Tsai} \\
  \vspace{8pt}
  \small
  \faMobile \hspace{.5pt} \href{tel:18589050735}{+1 (858) 905-0735}
  $\cdot$
  \faAt \hspace{.5pt} \href{mailto:ray@himetsai.com}{ray@himetsai.com}
  % $\cdot$
  % \faGithub \hspace{.5pt} \href{https://github.com/himetsai}{himetsai}
  % $\cdot$
  % \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/himetsai}{in/himetsai}
\end{center}

%----------- EDUCATION -----------

\section{Education}
\resumeSubHeadingListStart
  \resumeEducationHeading{University of Oxford}{Oxford, United Kingdom}{M.Sc. in Mathematical Sciences}{Sep 2025 \textbf{--} Jun 2026}
  \resumeItemListStart
    \resumeItem{\textbf{Dissertation:} \textit{Induced Subgraphs in Ramsey Graphs}, advised by Prof. Alex Scott}
    \resumeItem{\textbf{Relevant coursework:} Theories of Deep Learning, Probability on Graphs and Lattices, Probabilistic Combinatorics, Networks, Continuous Optimization}
  \resumeItemListEnd

  \vspace{3pt}

  \resumeEducationHeading{University of California San Diego}{La Jolla, CA}{B.Sc. in Mathematics-Computer Science (Honors with Highest Distinction), Math GPA: 3.98/4.0}{Sep 2021 \textbf{--} Jun 2025}
  \resumeItemListStart
    \resumeItem{\textbf{Honors Thesis:} \textit{Double Turán Problems}, advised by Prof. Jacques Verstraete}
    \resumeItem{\textbf{Relevant coursework:} Statistical Learning (Graduate), Extremal Combinatorics and Graph Theory (Honors), Discrete Geometry (Graduate), Complex Analysis (Graduate)}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%----------- TECHNICAL SKILLS -----------

% \section{Technical Skills}
% \resumeSubHeadingListStart
%   \small{\item{
%     \textbf{Languages:} Python, C/C++, SQL, JavaScript/TypeScript, C\#, \LaTeX \\
%     \textbf{Libraries \& Tools:} PyTorch, NumPy, Matplotlib, Jupyter, Git, React Native
%   }}
% \resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Adversarial Robustness via Smooth Activations} $|$ \textit{PyTorch, Python}}{Oxford, 2026}
    \resumeItemListStart
      \resumeItem{Proposed a unified theoretical view of FGSM and Input Gradient Regularization, explaining why smooth activations (GeLU, Softplus) prevent catastrophic overfitting in one-step adversarial training.}
      \resumeItem{Empirically confirmed that smooth activations recover near-full robustness at a fraction of the cost of standard adversarial training, extending prior results to new activation functions.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {MSI}{New Taipei City, Taiwan}
    {Software Engineer Intern}{Jul 2023 \textbf{--} Aug 2023}
    \resumeItemListStart
      \resumeItem{Fine-tuned Stable Diffusion model in PyTorch to generate realistic MSI product images for marketing; integrated model into \textit{MSI AI Artist}, a Windows desktop application for local AI image generation.}
      \resumeItem{Engineered automated installation pipeline for AI inference optimization backends, improving image generation throughput by 80\%.}
    \resumeItemListEnd

  \resumeSubheading
    {Kook}{San Diego, CA}
    {Co-founder \& Lead Software Engineer}{Dec 2021 \textbf{--} Dec 2022}
    \resumeItemListStart
      \resumeItem{Co-founded hardware-software startup for automated surfboard rental stations; secured UCSD Basement incubation and led 5-member engineering team.}
      \resumeItem{Built full-stack mobile application in React Native with SQL backend and NFC-based authentication, reducing rental initiation time by 75\%; developed embedded firmware in C++ on Arduino for hardware lock control.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {UC San Diego, Department of Mathematics}{La Jolla, CA}
    {Undergraduate Research Assistant}{Mar 2023 \textbf{--} Jun 2025}
    \resumeItemListStart
      \resumeItem{Conducted independent research in extremal graph theory under Prof. Jacques Verstraete; results on \textit{Double Turán Problems} constitute a manuscript in preparation for publication.}
      \resumeItem{Earned highest distinction in the UCSD Math Honors Program (awarded to $\sim$12 students annually).}
    \resumeItemListEnd

  \resumeSubheading
    {UC San Diego, Department of CSE}{La Jolla, CA}
    {Undergraduate Research Assistant}{Apr 2024 \textbf{--} Jun 2025}
    \resumeItemListStart
      \resumeItem{Studied graduate-level complexity theory and joined Prof. Russell Impagliazzo's research group on smooth boosting; explored connections between algorithmic fairness, computational complexity, and learning theory.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- AWARDS -----------

\section{Awards}
\resumeSubHeadingListStart
  \resumeSubSubheading{Physical Sciences Dean's Undergraduate Award for Excellence}{UC San Diego, 2025}
  \resumeItemListStart
    \resumeItem{Awarded to top undergraduates in Mathematics, Chemistry \& Biochemistry, and Physics for academic excellence and research promise. (\$1000)}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
